### 2019-12-11 README.Rmd
updated README

msBalance is a an R package for analysis of balance responses in people with and without multiple sclerosis (MS)

## Downloading from GitHub for development

@@

## Installing from GitHub for use

@@

>>>>

msBalance is a an R package for analysis of balance responses in people with and without multiple sclerosis (MS).
The source data were created by Jessie Huisinga, Ph.D., and collected by Daniel Peterson, Ph.D.
The analysis code was primarily developed by J. LUcas McKay, Ph.D., M.S.C.R.

## Getting msBalance

### Downloading from GitHub for development

@@

### Installing from GitHub for use

@@

## Using msBalance

The best way to get started is by using the `msBalance` vignette.
